Gov 50 Final Project

### 2022-11-18 article.Rmd
second visualization

Distill is a publication format for scientific and technical writing, native to the web.

Learn more about using Distill for R Markdown at <https://rstudio.github.io/distill>.

>>>>

## Project thoughts

I am interested in exploring the relationship between religious practice, party affliations, on people's attitude towards COVID restrictions and political views.

```{r}
library(tidyverse)
library(readr)
```

```{r}
ATP_W70 <- read.csv("ATP_W70FromR.csv")
```

```{r}
ATP_W70 <- ATP_W70 |> mutate (Pray = case_when(SPIRIT2_a_W70 >=1 & SPIRIT2_a_W70 <= 4 ~ '1')) |> mutate(Scripture = case_when(SPIRIT2_b_W70 >=1 & SPIRIT2_b_W70 <= 4 ~ '1')) |> mutate (Meditate = case_when(SPIRIT1_a_W70 >=1 & SPIRIT1_a_W70 <= 4 ~ '1')) 
```

```{r}
ATP_W70 <- ATP_W70 |> mutate(Opinions_on_SD = case_when(COVIDCONG4_W70 == 1 ~ "Open", COVIDCONG4_W70 == 2 ~ "Open with restictions", COVIDCONG4_W70 == 3 ~ "Closed"))|> mutate (college_edu = ifelse(F_EDUCCAT == 1, "College", "Not College")) |> mutate (PARTY_affliation = case_when(PARTY_W70 == 1 ~ "Republican", PARTY_W70 == 2 ~ "Democrat", PARTY_W70 == 3 ~ "Independent", PARTY_W70 == 4 ~ "Something else")) |> filter (PARTY_affliation %in% c("Republican", "Democrat"))
```
```{r}
Opinions <- ATP_W70 |> group_by( PARTY_affliation, Opinions_on_SD) |> summarise(n= n()) |> mutate (prop = n/ sum(n)) |> drop_na( PARTY_affliation, Opinions_on_SD)

```{r}
Opinions_plot <- Opinions |> ggplot(aes(x = Opinions_on_SD, y = prop, fill = PARTY_affliation)) + geom_col() + labs( X= "opinions on what the operatings status of places of worship should be according to Party affliation")

Opinions_plot
```

```{r}

Opinions_diff_by_edu <- ATP_W70 |> filter (PARTY_affliation %in% c("Republican", "Democrat")) |> group_by(PARTY_affliation, college_edu, Opinions_on_SD) |> summarise(n= n()) |> mutate (prop = n/ sum(n)) |> drop_na(Opinions_on_SD, PARTY_affliation) |> select (-n)|> pivot_wider(names_from = PARTY_affliation, values_from = prop) |> mutate (Diff_in_prop = Republican - Democrat)
knitr:: kable (Opinions_diff_by_edu)

Opinions_by_educ_plot <- Opinions_diff_by_edu|> ggplot(aes(x = Opinions_on_SD, y = Diff_in_prop, fill =  college_edu)) + geom_col(position = "dodge") + labs( X= "opinions on what the operatings status of places of worship should be according to Party affliation and college education")

Opinions_by_educ_plot
```

```

```{r}
Opinions_plot <- Opinions |> ggplot(aes(x = Opinions_on_SD, y = prop, fill = PARTY_affliation)) + geom_col() + labs( X= "opinions on what the operatings status of places of worship should be according to Party affliation")

Opinions_plot
```

```{r}

```
